Choosing Color Palettes for Statistical Graphics

### 2006-05-30 trunk/vcd/paper/Color/draft.Rnw
fixes by KH
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@543 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\setkeys{Gin}{width=0.8\textwidth}
\begin{figure}[p]
\begin{center}
<<pal-q-examples, fig=TRUE, height=4, width=6>>=
par(mfrow = c(2, 2), mar = c(0, 0, 3, 0))
pal(rainbow_hcl(4, start = 30, end = 300), main = "dynamic (30 - 300)")
pal(rainbow_hcl(4, start = 60, end = 240), main = "harmonic (60 - 240)")
pal(rainbow_hcl(4, start = 270, end = 150), main = "cold (270 - 150)")
pal(rainbow_hcl(4, start = 90, end = -30), main = "warm (90 - -30)")
@
\caption{\label{fig:pal-q-examples} Examples for qualitative palettes}
\end{center}
\end{figure}

>>>>

\setkeys{Gin}{width=0.8\textwidth}
\begin{figure}[p]
\begin{center}
<<pal-q-examples, fig=TRUE, height=4, width=6>>=
par(mfrow = c(2, 2), mar = c(0, 0, 3, 0))
pal(rainbow_hcl(4, start = 30, end = 300), main = "dynamic [30, 300]")
pal(rainbow_hcl(4, start = 60, end = 240), main = "harmonic [60, 240]")
pal(rainbow_hcl(4, start = 270, end = 150), main = "cold [270, 150]")
pal(rainbow_hcl(4, start = 90, end = -30), main = "warm [90, -30]")
@
\caption{\label{fig:pal-q-examples} Examples for qualitative palettes}
\end{center}
\end{figure}
